% standard-tabelle
\begin{tabularx}{\textwidth}{|X|X|X|X|}
	\hline
    content & in & 4 & spalten \\
    \hline
\end{tabularx}

% tabelle über mehrere seiten (header kommt automatisch)
% 3x 2cm-spalten
\begin{longtable}{*{3}{|p{2cm}}|}
	\hline
	\textbf{Titel} & \textbf{der} & \textbf{Spalten} \\
    \hline
    \endhead
    normaler & content & hier \\
    \hline
\end{longtable}

% alphabetische aufzählung
\begin{enumerate}[nolistsep, noitemsep, label=\alph*)]
	\item content
    \item content
\end{enumerate}

% code
\begin{minted}[mathescape=false, fontsize=\fontsize{9.5pt}{10.8pt}, xleftmargin=6mm, framesep=0mm, tabsize=4, linenos]{python}
import antigravity
\end{minted}

% eigene schriftgröße                      {  x  }{ 1.2*x }
\newcommand{\schriftgroessenname}{\fontsize{8.5pt}{10.2pt}}

% lange gleichungen (aligned)
\begin{align*}
	a &= b \\
    &= \nonterm{f} \lightning \\
%
% fallunterscheidung
	fib(n) &= \begin{cases}
                \quad fib(n - 1) + fib(n - 2) & \text{, falls $n > 2$} \\
                \quad 1 & \text{, sonst}
            \end{cases}
\end{align*}

% beweis ende
\nuffsaid

% baum
\begin{center}
	\begin{forest}
        qtree edges
        [$A$, name=NODE_A
        	[$B$ 
            	[$D$ ] 
                [$E$ ] 
			]
            [$C$, name=NODE_C
            	[$F$ ]
                [,.phantom]
			]
		]
%
		\draw[decorate,decoration={brace,amplitude=10pt}] (3,0) -- (3,-2.5);
        \node[anchor=west] at (3.5,-1.3) {Beschreibung};
%
		\draw[dashed, <->] (NODE_C) to [bend right=90] (NODE_A);
	\end{forest}
\end{center}

% graphen
\begin{center}
	\begin{tikzpicture}[node distance=3cm]
    	\node[graph node] (v1) {$v_1$};
        \node[graph node, above right=1.5cm and 2cm of v1] (v2) {$v_2$};
        \node[graph node, below right=1.5cm and 2cm of v1] (v3) {$v_3$};


		\draw[graph edge] (v1) -- (v2) node[edge weight] {12};
		\path[graph edge] (v1)  edge[bend left=20] node[edge weight] {2} (v3)
        		          (v3) edge[bend left=20] node[edge weight] {3} (v1);

		\draw[graph edge] (v2) -- (v3) node[edge weight] {1};
    \end{tikzpicture}
\end{center}

% typographie
\textbf{fett}
\textit{kursiv}
\underline{unterstrichen}
\texttt{monospace/code}












% font test
Neutra photo booth yuccie roof party, williamsburg sartorial art party iPhone sustainable fixie kogi. Bushwick kinfolk authentic, roof party blue bottle meditation banh mi cliche skateboard echo park. Artisan gastropub kombucha tilde retro sartorial. Cronut whatever brunch umami. Banjo butcher chartreuse marfa. Hella pabst iPhone shabby chic brunch. YOLO gentrify meditation, skateboard direct trade roof party butcher tumblr narwhal heirloom. Sustainable vinyl vice, whatever franzen pork belly actually pour-over gluten-free. Microdosing sartorial cray paleo next level messenger bag.


\newpage